Simulation pipeline

### 2021-07-22 Analysis/02_Simulation_pipeline.Rmd
Sim up

```{r}
## Creating the function for simulating equalizing
simulate.equalizing <- make.simulation.pipeline(type = "equalizing")
```

@@

```{r, eval = FALSE}
## Running one replicate
simulate.equalizing()
```

@@

For that we will use the custom `optim.replicate()` function which comes with one diagnosis function (checking if the variance for each metric is < 0.05) and one summarising (summarising the output of `simulate.equalizing()` for diagnosis) function

@@

```{r, eval = TRUE}
## Running the full optimisation
results <- optim.replicate(input.fun = simulate.equalizing,
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 1000,
                           stop.variance = 0.05,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_equalizing.rda")
```
> Note that you can use the parallel version by adding the argument `parallel = TRUE` that is automatised using the package `future` and `future.apply` which makes the whole process run on all your available cores but is way less verbose. Without using the parallel version, it takes roughly 10 hours (overnight) to run the analyses on an old 2.2Ghz 8GB core.

@@

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_equalizing.rda") #126
analyse.replicates("../Data/Processed/sim_equalizing.rda") #163
```

>>>>

```{r}
## Creating the function for simulating facilitation
simulate.facilitation <- make.simulation.pipeline(type = "facilitation")
```

@@

```{r, eval = FALSE}
## Running one replicate
simulate.facilitation()
```

@@

For that we will use the custom `optim.replicate()` function which comes with one diagnosis function (checking if the variance for each metric is < 0.05) and one summarising (summarising the output of `simulate.facilitation()` for diagnosis) function

@@

```{r, eval = TRUE}
## Running the full optimisation
results <- optim.replicate(input.fun = simulate.facilitation,
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 170,
                           stop.variance = 0.0001,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_facilitation.rda")
```
> Note that you can use the parallel version by adding the argument `parallel = TRUE` that is automatised using the package `future` and `future.apply` which makes the whole process run on all your available cores but is way less verbose. Without using the parallel version, it takes roughly 10 hours (overnight) to run the analyses on an old 2.2Ghz 8GB core.

@@

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140 -> #170
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_competition.rda") #126
analyse.replicates("../Data/Processed/sim_facilitation.rda") #163
```
